### 2014-07-07 tex/proofs.tex
Fixed a typo in the field initialization lemma
The reference compares proof is now nearly complete

\begin{lemma}
\label{lem:init}
If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow w_s s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
\end{lemma}

@@

%proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
\begin{lemma}
If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
\end{lemma}
There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch. Since the proofs for both rules are nearly identical, for clarity we will only prove the case for the $\cfgt{true}$ branch here. 
\begin{proof}
Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$. Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists $(g\ h) : s_\ell \rightarrow s_s$. 
Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$. In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that 
$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$

Case 1: Assume $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$. In this case, the equals - references true rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_T$. Since $(g\ h)$ is valid, we know that $\exists \lp \phi_0\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_0\rp \rp$, $\exists \lp \phi_1\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_1\rp \rp$, and that $\mathbb{S}\lp\phi_s\wedge\phi_0\wedge \phi_1\rp$ holds true. Observe that by applying theorem \ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$. Therefore, $\lp g\ h \rp: s_\ell^\prime \rightarrow s_s^\prime$ is a valid heap homomorphism, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$. Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $s_\ell^\prime \in \zeta_T \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$.
% Furthermore, since  and since we may conclude that $s_s^\prime \equiv \zeta_T$.

\end{proof}

>>>>

\begin{lemma}
\label{lem:init}
If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow_S s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
\end{lemma}

@@

%proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
\begin{lemma}
If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}$.
\end{lemma}
There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch. Since the proofs for both rules are nearly identical, for clarity we will only prove the case for the $\cfgt{true}$ branch here. 
\begin{proof}
Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$. Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists $(g\ h) : s_\ell \rightarrow s_s$. 
Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
%I'm not sure we actually use this fact anywhere
 %In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that 
%$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$

Case 1: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
$$\zeta_t = \zeta_T \setminus \{ s_f | \cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp \}$$ In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$. Since $(g\ h)$ is valid, we know that $\exists \lp \phi_0\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_0\rp \rp$, $\exists \lp \phi_1\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_1\rp \rp$, and that $\mathbb{S}\lp\phi_s\wedge\phi_0\wedge \phi_1\rp$ holds true. Observe that by applying theorem \ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$. Therefore, $\lp g\ h \rp: s_\ell^\prime \rightarrow s_s^\prime$ is a valid heap homomorphism, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$. Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $$s_\ell^\prime \in \zeta_t \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
Now we prove the case for the other direction. Consider the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$. Define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''. Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_g$ is only strengthened,  we know that:
$$\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\} $$
Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$. Because of the above conclusion, we know that $$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$ Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$. Because of this, and because of theorem \ref{thm:mutex}, we know that either all constraints $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp$$ are unsatisfiable, or that at least one constraint $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp$$ is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false, $\lp g\ h\rp$ is not a valid homomorphism, and $s_s^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: $$s_\ell^\prime \sqsubset s_s^\prime \Rightarrow s_\ell^\prime \in \zeta_t$$
Combining this with our previous result, we conclude that $$s_\ell^\prime \in \zeta_t \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$

Case 2: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
$$\zeta_f = \zeta_T \setminus \{ s_t | \cfgnt{L}_t \lp \cfgnt{r}_0\rp = \cfgnt{L}_t \lp \cfgnt{r}_1 \rp \}$$ 
This means that the lazy ``equals - references false" rule applies. The proof for the ``equals - references false" rule is highly similar to the proof for ``equals - references true", so we omit it for the sake of brevity. The result for this case is:
$$s_\ell^\prime \in \zeta_f \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$

Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that $$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$. By definition \ref{congruent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
\end{proof}
